Wind veer in Turbulent Ekman Flow - Part 2: Extrapolation to atmospheric scale separation

### 2024-10-10 write1/manuscript.tex
finished paragraph on Etling model

%ETLING MODEL 
Given a surface veering, a formulation for the velocity profile in the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. This simple model is compared to our DNS data and theoretical profiles in Fig.~\ref{fig:etling}.

\begin{figure}
  \includegraphics[width=0.5\textwidth]{../plot/etling_direction_1.pdf} 
  \includegraphics[width=0.5\textwidth]{../plot/etling_magnitude_1.pdf}
  \caption{}
  \label{fig:etling} 
\end{figure}
outlined in 
\textbf{Compare} to Emeis (2002) and Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;

>>>>

%ETLING MODEL 
A two-layer model consolidating both the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. Given a surface veering and a matching height (extent of the logarithmic layer), a formulation for the velocity profile across both the logarithmic and the outer layer is obtained. A comparison using the surface veering based on our model and a matching height of $z_\text{prandtl}=0.05\delta$, which gives better results than the matching height of $0.1\delta$ suggested by \cite{etling:2008}, is shown in Fig.~\ref{fig:etling}. 
% 
The overall shape of velocity magnitude is matched apart from the viscous and buffer layer (cf. Fig.~\ref{fig:etling}b) that is neglected by the two-layer model. However, quantitative departures on the order of 10-20\% occur across the inner layer: it turns out that the non-rotating profile, of the two-layer model in the logarithmic region yields too low overall velocity as the spanwise component contributes to the velocity across the inner layer. 
% 
Deviations also occur with respect to wind direction; despite the rather low matching height, a substantial fraction of the rotation occurs within the lower part of the ABL and about 20\% of the wind veer is not captured by the two-layer model. 
% 
As the overall veer is given, the non-captured veer close to the surface is then compensated across the logarithmic layer. In the upper part of the boundary layer, both profiles match well. 
%

\begin{figure}
  \includegraphics[width=0.5\textwidth]{../plot/etling_direction_1.pdf} 
  \includegraphics[width=0.5\textwidth]{../plot/etling_magnitude_1.pdf}
  \caption{Comparison of the DNS data (dashed lines) with the two-layer model proposed by Etling (solid lines) for different Reynolds number. Left panel shows the relative wind veer, right panel shows the velocity magnitude. The etling model is calibrated by the surface veer from the DNS and roughness parameter for the Etling model is chosen according to the correction factor $\exp{\kappa A}$ such that the total veer and velocity magnitude agree. DNS profile in the buffer layer, defined here as $z^+<30$ are shown as opaque dashed lines as the two-layer model does not consider viscous effects.}
  \label{fig:etling} 
\end{figure}
outlined in 
\textbf{Compare} Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;

### 2024-10-10 write2/manuscript_part2_2024.tex
finished paragraph on Etling model

\begin{abstract}
  % Introduction % Theoretical profile
  The atmospheric boundary layer is characterized by a logarithmic increase of the wind speed in the surface layer and a turning of the wind vector aloft. The simplest canonical configuration featuring both \emph{a logarithmic layer and the wind turning} is Ekman flow. A formulation of the mean velocity profile was derived from scaling considerations and calibrated using direct numerical simulation in part I of this work. Here, we explore the extrapolation to atmospheric Reynolds number (Re) using large-eddy simulation (LES).
  % Case desription and setup
  Theoretical profiles of the wind vector are compared to the theoretical reference at intermediate Re, which necessitates consideration of viscous effects % [not required in abstract] (usually neglected in LES) 
  along with modifications to the standard bottom boundary condition.
  % Results and Discussion
  Analysis of the grid convergence for higher resolution unveils a convergence of LES data towards the theoretical profiles for intermediate and high Re. The LES thus confirm that (i) the spanwise velocity scales as $\left.Re_\tau\right.^{-1}$, where $Re_\tau$ is the friction Reynolds number, and (ii) one third of the wind veer is confined to the surface layer.
  % [this level of detail is not needed in the abstract] (the lowest 10\,\% of the boundary layer) 
  % Conclusions
  Such agreement of the theoretical formulation and LES data raises confidence in the underlying scaling assumptions and thus reinforces the utility of the theoretical profiles as a reference for intermediate and a quasi-reference for both idealized simulation and field observation.
%

>>>>

\begin{abstract}
  % Introduction % Theoretical profile
  The atmospheric boundary layer is characterized by a logarithmic increase of the wind speed in the surface layer and a turning of the wind vector aloft. The simplest canonical configuration featuring both \emph{a logarithmic layer and the wind turning} is Ekman flow. A formulation of the mean velocity profile was derived from scaling considerations and calibrated using direct numerical simulation in part I of this work. Here, we explore the extrapolation to atmospheric Reynolds number (Re) using large-eddy simulation (LES).
  % Case desription and setup
  Theoretical profiles of the wind vector are compared to the theoretical reference at intermediate Re, which necessitates consideration of viscous effects % [not required in abstract] (usually neglected in LES) a
  along with modifications to the standard bottom boundary condition.
  % Results and Discussion
  Analysis of the grid convergence for higher resolution unveils a convergence of LES data towards the theoretical profiles for intermediate and high Re. The LES thus confirm that (i) the spanwise velocity scales as $\left.Re_\tau\right.^{-1}$, where $Re_\tau$ is the friction Reynolds number, and (ii) one third of the wind veer is confined to the surface layer.
  % [this level of detail is not needed in the abstract] (the lowest 10\,\% of the boundary layer) 
  % Conclusions
  Such agreement of the theoretical formulation and LES data raises confidence in the underlying scaling assumptions and thus reinforces the utility of the theoretical profiles as a reference for intermediate and a quasi-reference for both idealized simulation and field observation.
%
